---
title: "Using the Twitter API for Academic Research: A Brief Introduction"
author: "Christian Staal Bruun Overgaard"
date: "September 7, 2022"
output: html_document
---

## Introduction: Getting started
*Load packages*

```{r}
#install.packages("tidyverse") #you only need to install each package once
library(tidyverse) #you need to load the packages each time you re-open R
library(academictwitteR)
```

*Set bearer token*

```{r}
set_bearer()
```

## Collecting tweets and metadata

*Collect tweets*

```{r}
tweets <- 
  get_all_tweets(
    query = "ukraine", #the word you're searching for
    start_tweets = "2022-06-06T00:00:00Z",
    end_tweets = "2022-06-06T10:00:00Z",
    n = 201, #the max number of tweets you want to collect
    data_path = "my_new_datapath" #for the sake of example (only needed for large queries)
  )

```

*Saving the dataframe*

```{r}
#save(tweets,file="tweets_from_api_workshop.Rda") #run if you want to save the "tweets" object on your computer.
```

*Select relevant columns*

```{r}
mydata <- tweets |>
  dplyr::select(id, text, created_at, starts_with("public_metrics"))

head(mydata)
```

*Multiple words to search for*

```{r}
my_words <- c("ukraine", "putin", "zelensky")

tweets2 <-
  get_all_tweets(
    query = my_words, #use vector of terms
    start_tweets = "2022-06-06T00:00:00Z",
    end_tweets = "2022-06-06T10:00:00Z",
    n = 50
  ) |>
  dplyr::select(id, text, created_at, starts_with("public_metrics"))

#tweets2$public_metrics
```

Specify more details using `build_query`

```{r}
my_query <- build_query(query = 
                         my_words,
                         lang = "en")

tweets3 <-
  get_all_tweets(query = my_query,
    start_tweets = "2016-06-06T00:00:00Z",
    end_tweets = "2022-08-06T10:00:00Z",
    n = 50,
    verbose = FALSE, #hide some output
    is_retweet = FALSE, #exclude retweets
    remove_promoted = TRUE, #discard sponsored content
    has_geo = TRUE) |> #only show english content
  dplyr::select(id, text, created_at, starts_with("public_metrics"))

glimpse(tweets3)
#head(tweets3) #another way of getting a quick glimpse of the data
```

For more info, see `?get_all_tweets`.

## Counting the number of tweets that fit certain criteria

*Count*

```{r}
count_feb_2022 <- count_all_tweets(my_words, "2022-02-01T00:00:00Z", "2022-03-01T00:00:00Z") #only one month

#count_feb_2022
value_feb_2022 <- round(sum(count_feb_2022$tweet_count)/(10^6), digits = 0)

cat("2022:", value_feb_2022, "Million")
```

*Compare with Feb 2021*

```{r}
count_feb_2021 <- count_all_tweets(my_words, "2021-02-01T00:00:00Z", "2021-03-01T00:00:00Z") #only one month

#count_feb_2022
value_feb_2021 <- round(sum(count_feb_2021$tweet_count)/(10^6), digits = 0)

cat("2021:", value_feb_2021, "Million")
```


*Bonus: Counting tweets from a longer period of time*

```{r}
count1 <- count_all_tweets(my_words, "2022-01-01T00:00:00Z", "2022-04-01T00:00:00Z")

count2 <- count_all_tweets(my_words, "2022-04-01T00:00:00Z", "2022-06-1T00:00:00Z")

count3 <- count_all_tweets(my_words, "2022-06-01T00:00:00Z", "2022-08-28T00:00:00Z")

combined_count <- bind_rows(count1, count2, count3)

value2022 <- round(sum(combined_count$tweet_count)/(10^6), digits = 0) # millions
cat("2022:", value2022, "Million")
```

Let's see how that compares to the same period of 2021:

```{r}
count1 <- count_all_tweets(my_words, "2021-01-01T00:00:00Z", "2021-04-01T00:00:00Z", verbose = FALSE)

count2 <- count_all_tweets(my_words, "2021-04-01T00:00:00Z", "2021-06-1T00:00:00Z", verbose = FALSE)
count3 <- count_all_tweets(my_words, "2021-06-01T00:00:00Z", "2021-08-28T00:00:00Z", verbose = FALSE)

combined_count2 <- bind_rows(count1, count2, count3)
value2021 <- round(sum(combined_count2$tweet_count)/(10^6), digits = 0)
cat("2021:", value2021, "Million")
```


## Tweets from specific users
Let's look at the average number of Retweets for President Zelensky's tweets for 2022 and 2021.

*2022*

```{r}
zelensky2022 <-
  get_all_tweets(users = "ZelenskyyUa",
    start_tweets = "2022-01-01T00:00:00Z",
    end_tweets = "2022-08-28T10:00:00Z",
    n = 1000
  ) |>
  dplyr::select(id, text, created_at, starts_with("public_metrics"))

value2021 <- round(mean(zelensky2022$public_metrics$retweet_count), digits = 0)

cat("2022:", value2021, "Retweets on average")
```

*2021*

```{r}
zelensky2021 <-
  get_all_tweets(users = "ZelenskyyUa",
    start_tweets = "2021-01-01T00:00:00Z",
    end_tweets = "2021-08-28T10:00:00Z",
    n = 1000
  ) |>
  dplyr::select(id, text, created_at, starts_with("public_metrics"))

round(mean(zelensky2021$public_metrics$retweet_count), digits = 0)

value2021 <- round(mean(zelensky2021$public_metrics$retweet_count), digits = 0)

cat("2021:", value2021, "Retweets on average")
```




